Flatiron cleaning

### 2023-01-06 Rmd/Response to reviewers.Rmd

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp,  -->
<!--                    data=Frontline %>%  -->
<!--                      filter(therapy == "Upfront Chemo") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Chemo", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp,  -->
<!--                    data=Frontline %>%  -->
<!--                      filter(therapy == "Upfront Surgery") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Surgery", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->
<!-- ``` -->
<!-- <br> -->
<!-- <br> -->

***

# IV.Hazard Ratio
## Multivariable
## Adjusted by other drug
## <span style="color:green">**Table 3 HR Multivariable**</span>

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking+ dx_year_cat`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H Table 3 HR Multivariable adj deb}
coxph(Surv(time = tbl2$month_at_os_from_treatment,
             event = tbl2$vital_status
           ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking,
      data =  tbl2)  %>%
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking,
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +
        imp_stagecat + strata(histology) + imp_debulking,
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +
        strata(imp_stagecat) + strata(histology) + imp_debulking,
      data = tbl3) %>%
  cox.zph()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + dx_year_cat`
```{r}
tbl2 <- Frontline %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- Frontline %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ 
          RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + dx_year_cat,
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

PH assumption Upfront Chemo
```{r prop H Table 3 HR Multivariable non adj deb}
coxph(Surv(time = tbl2$month_at_os_from_treatment,
             event = tbl2$vital_status
           ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology,
      data = tbl2)  %>%
  cox.zph()
```

PH assumption Upfront Surgery
```{r}
coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology,
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +
        imp_stagecat + strata(histology),
      data = tbl3) %>%
  cox.zph()

coxph(Surv(time = tbl3$month_at_os_from_treatment,
             event = tbl3$vital_status
           ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +
        strata(imp_stagecat) + strata(histology),
      data = tbl3) %>%
  cox.zph()
```
<br>
<br>

***

<br>

# Complete case HR analysis
```{r}
Frontline <- Frontline %>% distinct(patientid, .keep_all = TRUE) %>% 
  mutate(comp_cases = case_when(
    is.na(stagecat) |
      is.na(debulking)                     ~ "excluded",
    TRUE                                   ~ "complete cases"
  ))
complete_cases <- Frontline %>% filter(comp_cases == "complete cases")
```

## <span style="color:green">**Table S1 HR patient characteristics by inclusion in complete-case**</span>
```{r}
Frontline %>%
  select(c(dx_year_cat, raceeth,
           ageatdx,
           bmi_at_dx, bmi_cat,
           histology1, "histology",
           "stagecat", imp_stagecat,
           therapy,
           debulking, imp_debulking,
           comp_cases)) %>%
  tbl_summary(by = comp_cases) %>%
  bold_labels() %>% add_p() %>% bold_p()
```
<br>

## Multivariable
### RDI group
## <span style="color:green">**Table S2 HR Multivariable complete cases**</span>

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking + dx_year_cat`
```{r}
tbl2 <- complete_cases %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- complete_cases %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + strata(histology) + debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<!-- PH assumption Upfront Chemo -->
<!-- ```{r prop H Table S2 HR Multivariable complete cases adj deb} -->
<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
<!--              event = tbl2$vital_status -->
<!--            ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, -->
<!--       data =  tbl2)  %>% -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- PH assumption Upfront Surgery -->
<!-- ```{r} -->
<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + debulking, -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->

<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + strata(histology) + debulking, -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->

<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + strata(stagecat) + strata(histology) + debulking, -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->
<!-- ``` -->

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + dx_year_cat`
```{r}
tbl2 <- complete_cases %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- complete_cases %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + strata(histology) + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

<!-- PH assumption Upfront Chemo -->
<!-- ```{r prop H Table S2 HR Multivariable complete cases non adj debonly} -->
<!-- coxph(Surv(time = tbl2$month_at_os_from_treatment, -->
<!--              event = tbl2$vital_status -->
<!--            ) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, -->
<!--       data =  tbl2)  %>% -->
<!--   cox.zph() -->
<!-- ``` -->

<!-- PH assumption Upfront Surgery -->
<!-- ```{r} -->
<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + histology, -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->

<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +  -->
<!--         stagecat + strata(histology), -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->

<!-- coxph(Surv(time = tbl3$month_at_os_from_treatment, -->
<!--              event = tbl3$vital_status -->
<!--            ) ~ RDI_carbo_adj_grp + raceeth + ageatdx +  -->
<!--         strata(stagecat) + strata(histology), -->
<!--       data =  tbl3) %>% -->
<!--   cox.zph() -->
<!-- ``` -->
<br>
<br>

***
<br>

# Serous histology
```{r serous filter}
serous <- Frontline %>% filter(histology == "Serous") 
```

<!-- ## KM -->
<!-- ```{r serous KM, fig.height = 7} -->
<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_neo_grp,  -->
<!--                    data=serous %>%  -->
<!--                      filter(therapy == "Upfront Chemo") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Chemo", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp,  -->
<!--                    data=serous %>%  -->
<!--                      filter(therapy == "Upfront Chemo") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Chemo", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

### 2023-01-06 Rmd/Response to reviewers.Rmd

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->

<!-- ggsurvplot(survfit(Surv(month_at_os_from_treatment, vital_status) ~ RDI_carbo_adj_grp,  -->
<!--                    data=serous %>%  -->
<!--                      filter(therapy == "Upfront Surgery") %>% -->
<!--                      distinct(patientid, .keep_all = TRUE) -->
<!--                    ), -->
<!--            title = "OS from treatment carboplatin \nUpfront Surgery", -->
<!--            font.main = c(24, "bold", "black"), -->
<!--            font.x = c(20, "bold", "black"), font.y = c(20, "bold", "black"), -->
<!--            font.legend = c(14, "bold", "black"), font.tickslab = c(18, "bold", "black"), -->
<!--            size = 1.5, -->

<!--            pval=TRUE, -->
<!--            # legend.labs=c(""), -->
<!--            # palette = c("black", "green","blue", "red"), -->
<!--            # Add risk table -->
<!--            risk.table = "abs_pct", risk.table.title = "Risk table (number(%))", -->
<!--            risk.table.y.text = FALSE, risk.table.fontsize = 3, tables.height = 0.3, -->
<!--            tables.theme = theme_survminer(base_size = 5, -->
<!--                                           font.main = c(16, "bold", "black"), -->
<!--                                           font.x = c(16, "bold", "black"), -->
<!--                                           font.y = c(16, "bold", "transparent"), -->
<!--                                           font.tickslab = c(19, "bold", "black") -->
<!--            ), -->

<!--            legend.title = "", xlab = "Time (in months)" -->
<!-- ) + guides(colour = guide_legend(ncol = 1)) -->
<!-- ``` -->

## HR
### Imputed data
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking + dx_year_cat`
```{r}
tbl2 <- serous %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- serous %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + dx_year_cat`
```{r}
tbl2 <- serous %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- serous %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ 
          RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + dx_year_cat,
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

### Complete cases
```{r}
serous_complete <- complete_cases %>% filter(histology == "Serous")
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking + dx_year_cat`
```{r}
tbl2 <- serous_complete %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- serous_complete %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + dx_year_cat`
```{r}
tbl2 <- serous_complete %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- serous_complete %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

***
<br>

# Others histology
```{r other filter}
other_hist <- Frontline %>% filter(histology == "Others")
```

## HR
### Imputed data
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking + dx_year_cat`
```{r}
tbl2 <- other_hist %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- other_hist %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + dx_year_cat`
```{r}
tbl2 <- other_hist %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- other_hist %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ 
          RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + dx_year_cat,
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

### Complete cases
```{r}
others_complete <- complete_cases %>% filter(histology == "Others")
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking + dx_year_cat`
```{r}
tbl2 <- others_complete %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- others_complete %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status
             ) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + dx_year_cat`
```{r}
tbl2 <- others_complete %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + stagecat + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- others_complete %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(stagecat) + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl_stack(list(tbl21, tbl31),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

# Stratified by BMI
## Underweight and normal weight + Overweight vs Obese
```{r}
Frontline <- Frontline %>% 
  mutate(bmi_strat = case_when(
    bmi_cat == "Underweight and normal weight" |
    bmi_cat == "Overweight"                          ~ "not obese",
    bmi_cat == "Obese"                               ~ "obese"
  )) %>% 
  mutate(bmi_strat2 = case_when(
    bmi_cat == "Underweight and normal weight"       ~ "Underweight and normal weight",
    bmi_cat == "Overweight" |
    bmi_cat == "Obese"                               ~ "Overweight or obese"
  ))
```

`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking+ dx_year_cat`
```{r}
not_obese <- Frontline %>% 
  filter(bmi_strat == "not obese")
obese <- Frontline %>% 
  filter(bmi_strat == "obese")

tbl2 <- not_obese %>%
  filter(therapy == "Upfront Chemo")
tbl21 <- 
  coxph(Surv(time = tbl2$month_at_os_from_treatment, 
             event = tbl2$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl2) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl3 <- not_obese %>%
  filter(therapy == "Upfront Surgery")
tbl31 <- 
  coxph(Surv(time = tbl3$month_at_os_from_treatment, 
             event = tbl3$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl3) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

tbl4 <- obese %>%
  filter(therapy == "Upfront Chemo")
tbl41 <- 
  coxph(Surv(time = tbl4$month_at_os_from_treatment, 
             event = tbl4$vital_status) ~ RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking + dx_year_cat, 
        data =  tbl4) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")
tbl5 <- obese %>%
  filter(therapy == "Upfront Surgery")
tbl51 <- 
  coxph(Surv(time = tbl5$month_at_os_from_treatment, 
             event = tbl5$vital_status) ~ RDI_carbo_adj_grp + raceeth + ageatdx + 
          strata(imp_stagecat) + strata(histology) + imp_debulking + dx_year_cat, 
        data =  tbl5) %>%
  tbl_regression(exponentiate = TRUE) %>% 
  bold_p(t = .05) %>% add_nevent(location = "level") %>% add_n(location = "level")

a <- tbl_merge(list(tbl21, tbl41), tab_spanner = c("not obese", "obese"))
b <- tbl_merge(list(tbl31, tbl51))
tbl_stack(list(a, b),
          group_header = c("Upfront Chemo", "Upfront Surgery")) %>%
  bold_labels() %>%
  italicize_levels()
```

## Underweight and normal weight vs Overweight + Obese
`RDI_carbo_neo_grp + RDI_carbo_adj_grp + raceeth + ageatdx + imp_stagecat + histology + imp_debulking+ dx_year_cat`
```{r}
normal <- Frontline %>% 
  filter(bmi_strat2 == "Underweight and normal weight")
overweight <- Frontline %>% 
  filter(bmi_strat2 == "Overweight or obese")
